\section{Some Definitions}

% TODO rearrange the order of the definitions

\subsection{Channel}

      \begin{frame}
            \frametitle{Channel}
            \begin{definition}[channel]
                  A channel has a sender and a receiver.
                  \pause


                  A message is a finite sequence of characters.
                  The sender sends a message to the receiver.
                  \begin{figure}[h!]
                        \tikzstyle{vertex}=[fill=black!25,minimum size=20pt,inner sep=0pt]
                        \tikzstyle{message}=[inner sep=0pt]
                        \tikzstyle{edge} = [draw,thick,-]
                        \tikzstyle{weight} = [font=\small]
                        \begin{tikzpicture}[scale=1, auto,swap]
                              % Draw a 7,11 network
                              % First we draw the vertices
                              \foreach \pos/\name in {{(0,0)/sender}, {(3,0)/receiver}}
                                    \node[vertex] (\name) at \pos {$\name$};
                              \foreach \pos/\name in {{(0,1)/abcde}, {(3,1)/acbde}}
                                    \node[message] (\name) at \pos {$\name$};
                              % Connect vertices with edges and draw weights
                              \foreach \source/ \dest in {sender/receiver}
                              \path[edge] (\source) -- node[weight]{} (\dest);
                        \end{tikzpicture}
                  \end{figure}
                  \pause
                  
                  The receiver receives message and decode it.
                  \pause

                  However, in the procedure of send and receive, the channel may introduce some errors. For instance, here, character $b$ is decoded into $c$. 
            \end{definition}
      \end{frame}

      \begin{frame}
            \frametitle{Channel}
            \begin{definition}[confusable]
                  Given two characters $a$, $b$. If $a$ and $b$ have chance to be decoded into a same character say $c$, we say $a$ and $b$ are confusable.

                  For a two messages of length $n$, say $a_{1}a_{2}\dots a_{n}$, $b_{1}b_{2}\dots b_{n}$ is confusable if and only if $a_{i}$ and $b_{i}$ are confusable for every $i$.
            \end{definition}
            \pause
            \begin{definition}[rate of channel]
                  The rate of channel actually represent how many distinct character can be send per unit time.

                  Given a channel that could send $r$ distinct characters per unit time. And send message with length $n$, so the number of distinct messages the channel can send is $r^{n}$.

                  \pause

                  Conversely, given a channel that could send $m$ distinct messages with length $n$.
                  And could be able to send only one character per unit time.
                  The rate of channel is $\sqrt[n]{m}$.

                  Here, we do not care about how much characters. We only care about the number of all messages we can send.
                  
            \end{definition}
      \end{frame}

      \begin{frame}
            \frametitle{Channel}
            \begin{definition}[zero error rate]
                  Given a channel which could transfer messages of length $n$.

                  We want to find the maximum set of messages $M$ that no two of them is confusable.

                  \begin{equation}
                        \text{zero error rate} = \max_{M} \sqrt[n]{|M|}
                  \end{equation}
            \end{definition}
      \end{frame}

      \begin{frame}
            \frametitle{Channel}
            If given a set of characters $S$, and some of the characters could be confusable.

            We want to find
            \begin{equation}
                  \sup_{n} \left\{
                        \text{zero error rate of channel with length $n$ and $S$ as characters}
                  \right\}
            \end{equation}

            And we call this the shannon Capacity and denoted by $\Theta(S)$.

            Clearly, shannon Capacity is actually a function of the set of characters. So, we want a more abstract way to represent the characters.
      \end{frame}

\subsection{Graph Representation of Characters}

      \begin{frame}
            \frametitle{Graph Representation Of Characters}
            \begin{definition}[graph] \label{def:graph}
                  A graph $ G $ is a set of vertices with a set of edges connecting pairs of vertices.

                  \begin{figure}[h!]
                        \tikzstyle{vertex}=[circle,fill=black!25,minimum size=20pt,inner sep=0pt]
                        \tikzstyle{edge} = [draw,thick,-]
                        \tikzstyle{weight} = [font=\small]
                        \begin{tikzpicture}[scale=1, auto,swap]
                              % Draw a 7,11 network
                              % First we draw the vertices
                              \foreach \pos/\name in {{(0,2)/a}, {(2,1)/b}, {(4,1)/c},
                                    {(0,0)/d}, {(3,0)/e}, {(2,-1)/f}, {(4,-1)/g}}
                                    \node[vertex] (\name) at \pos {$\name$};
                              % Connect vertices with edges and draw weights
                              \foreach \source/ \dest in {b/a, c/b,d/a,d/b,
                                    e/b, e/c,e/d,
                                    f/d,f/e,
                                    g/e,g/f}
                              \path[edge] (\source) -- node[weight]{} (\dest);
                        \end{tikzpicture}
                        \label{fig:graphDefinitionExample}
                        \caption{An example of a graph.}
                  \end{figure}
            \end{definition}
      \end{frame}

      \begin{frame}
            \frametitle{Graph Representation Of Characters}
            \begin{definition}\label{def:graphRepresetationOfChannel}
                  Given a channel that sending $\{1,2,\dots,n\}$ as characters. And some characters $i$ and $j$ could be confused with each other.

                  Then the graph representation of the characters is the graph with vertices $\{1,2,\dots,n\}$ and edges $(i,j)$ if and only if $i$ and $j$ could be confused with each other.
            \end{definition}

            Accordingly, there is the corresponding way that using graphs to represent a message zero error rate and Shannon Capacity.
      \end{frame}

\subsection*{Product Graph}

      \begin{frame}
            \frametitle{Product Graph}
            \begin{definition}[graph product]\label{def:graphProduct}
                  The product of two graphs can be considered as send a pair of characters $(x,y)$ as one message. So, we have a channel that send messages of length $2$.

                  \pause

                  Recall that before, $2$ messages is confusable means that they can be decoded into the same message, which means every characters the two channel use need to be confusable.

                  Given two graph $ G $ and $ H $. The graph product $ G \times H $ is the graph with vertices $ V(G \times H) = V(G) \times V(H) $ in which $ (x,y) $ is adjacent to $ (x',y') $ in $ G \times H $ if and only if $ x $ is adjacent to $ x' $ in $ G $ and $ y $ is adjacent to $ y' $ in $ H $.
      
                  \pause

                  A graph $ G $ product itself for $ n $ times will always be denoted by $ G^n $.

                  Which means we could use $ G^n $ to represent messages of a channel with length $n$.
            \end{definition}
      \end{frame}

\subsection*{Alpha Function}

      \begin{frame}
            \frametitle{$\alpha(G)$}
            \begin{definition}[$\alpha(G)$]\label{def:alpha}
                  The $\alpha(G)$ represent the maximum number of characters or message that could not be confused with each other in graph $G$.

                  If $G$ represent a set of messages, $\alpha(G)$ is just the zero error rate we have defined before.

                  \pause

                  Given a graph $ G $. Given a subgraph $ H $ of $ G $, such that every vertex of $ H $ is not connected in $ G $. Then $ \alpha(G) $ is the maximum number of vertices of $ H $.
                  \tikzstyle{vertex}=[circle,fill=black!25,minimum size=20pt,inner sep=0pt]
                  \tikzstyle{selected vertex}=[circle,fill=red!25,minimum size=20pt,inner sep=0pt]
                  \tikzstyle{edge} = [draw,thick,-]
                  \tikzstyle{weight} = [font=\small]
                  \begin{figure}[h!]
                        \begin{tikzpicture}[scale=1, auto,swap]
                              % Draw a 7,11 network
                              % First we draw the vertices
                              \foreach \pos/\name in {{(0,1)/a}, {(2,1)/b}, {(4,1)/c},
                                    {(0,0)/d}, {(3,0)/e}, {(2,-1)/f}, {(4,-1)/g}}
                                    \node[vertex] (\name) at \pos {$\name$};
                              \foreach \pos/\name in {{(0,1)/a}, {(4,1)/c},
                                    {(2,-1)/f}}
                                    \node[selected vertex] (\name) at \pos {$\name$};
                              % Connect vertices with edges and draw weights
                              \foreach \source/ \dest in {b/a, c/b,d/a,d/b,
                                    e/b, e/c,e/d,
                                    f/d,f/e,
                                    g/e,g/f}
                              \path[edge] (\source) -- node[weight]{} (\dest);
                        \end{tikzpicture}
                        \label{fig:alphaGExample}
                        \caption{Example of $ \alpha(G) $. Here $ \alpha(G) = 3 $.}
                  \end{figure}
            \end{definition}
      \end{frame}

\subsection{Shannon Capacity}

      \begin{frame}
            \frametitle{Shannon Capacity}
            \begin{definition}[Shannon Capacity]\label{def:shannonCapacity}
                  Recall that Shannon Capacity is 
                  \begin{equation}
                        \sup_{n} \left\{
                              \text{zero error rate of channel with length $n$ and $S$ as characters}
                        \right\}
                  \end{equation}

                  Use the graph $G$ to represent the set of characters, the Shannon capacity $ \Theta(G) $ is defined by
                  \begin{equation}
                        \Theta(G) = \sup_{n} \sqrt[n]{\alpha(G^n)} 
                  \end{equation}

            \end{definition}
      \end{frame}
