\subsection{\texorpdfstring{Channel \& Graph}{Channel and Graph}}

\subsubsection*{Channel}

      \begin{frame}
            \frametitle{Channel}
            \begin{definition}[channel]
                  Characters is a finite set.

                  A message is a finite sequence of characters.

                  A channel has a sender and a receiver.
                  The sender sends a message to the receiver.
                  \begin{figure}[h!]
                        \tikzstyle{vertex}=[fill=black!25,minimum size=20pt,inner sep=0pt]
                        \tikzstyle{message}=[inner sep=0pt]
                        \tikzstyle{edge} = [draw,thick,-]
                        \tikzstyle{weight} = [font=\small]
                        \begin{tikzpicture}[scale=1, auto,swap]
                              % Draw a 7,11 network
                              % First we draw the vertices
                              \foreach \pos/\name in {{(0,0)/sender}, {(3,0)/receiver}}
                                    \node[vertex] (\name) at \pos {$\name$};
                              \foreach \pos/\name/\la in {{(0,0.7)/abcde/a\textbf{\textit{bc}}de}, {(3,0.7)/acbde/a\textbf{\textit{cb}}de}}
                                    \node[message] (\name) at \pos {\la};
                              % Connect vertices with edges and draw weights
                              \foreach \source/ \dest in {sender/receiver}
                              \path[edge] (\source) -- node[weight]{} (\dest);
                        \end{tikzpicture}
                  \end{figure}
                  \pause
                  
                  The receiver receives message and decode it.
                  \pause

                  However, in the procedure of send and receive, the channel may introduce some errors. For instance, here, character $b$ is decoded into $c$. 
            \end{definition}
      \end{frame}

\subsubsection*{Confusable}

      \begin{frame}
            \frametitle{Confusable}
            \begin{definition}[confusable]
                  Given two distinct characters $a$, $b$. If $a$ and $b$ have chance to be \textbf{decoded into a same character} say $c$, we say $a$ and $b$ are \textbf{confusable}.

                  For a two distinct messages of length $n$, say $a_{1}a_{2}\dots a_{n}$, $b_{1}b_{2}\dots b_{n}$ is confusable if and only if $a_{i}$ and $b_{i}$ are \textbf{confusable} or \textbf{same} for every $i$.
            \end{definition}
      \end{frame}

\subsubsection*{Rate of Channel}

      \begin{frame}
            \frametitle{Rate of Channel}

            \begin{definition}[rate of channel]
                  The rate of channel actually represent how many \textbf{distinct character} can be send \textbf{per unit time}.

                  Given a channel that could send $r$ distinct characters per unit time. And send message for $n$ unit time, so the number of distinct messages the channel can send is $r^{n}$.

                  \pause

                  \vspace{0.5em}

                  Conversely, given a channel that could send $m$ \textbf{distinct messages} in $n$ \textbf{unit time}.
                  Then the rate of channel is $\sqrt[n]{m}$.
                  
            \end{definition}
      \end{frame}

\subsubsection*{Zero Error Rate of Channel}

      \begin{frame}
            \frametitle{Zero Error Rate of Channel}
            \begin{definition}[zero error rate]
                  Given a channel that could send messages in $n$ unit time.

                  We want to find the maximum set of messages $M$ that \textbf{no two of them is confusable}.
                  Which means if we send these messages then, there is no chance of get an error.

                  \begin{equation}
                        \text{zero error rate} = \max_{M} \sqrt[n]{|M|}
                  \end{equation}
            \end{definition}
      \end{frame}

      \begin{frame}
            \frametitle{Zero Error Rate of Channel}
            
            \begin{definition}
                  If given a set of characters $S$, and some of the characters could be confusable.

                  In the reality, we usually do not fix $n$, so the thing we really want to find is
                  
                  \begin{equation}
                        \sup_{n} \left\{
                              \text{zero error rate of channel send messages for $n$ unit time}
                        \right\}
                  \end{equation}

                  And we call this the shannon Capacity and denoted by $\Theta(S)$.
            \end{definition}

            Clearly, shannon Capacity is actually a function of the set of characters. So, we want a more abstract way to represent the characters.
      \end{frame}

\subsubsection*{Graph}

\begin{frame}
      \frametitle{Graph Representation Of Characters}
      \begin{definition}[graph] \label{def:graph}
            A graph $ G $ is a set of vertices with a set of edges connecting pairs of vertices.

            \begin{figure}[h!]
                  \tikzstyle{vertex}=[circle,fill=black!25,minimum size=20pt,inner sep=0pt]
                  \tikzstyle{edge} = [draw,thick,-]
                  \tikzstyle{weight} = [font=\small]
                  \begin{tikzpicture}[scale=1, auto,swap]
                        % Draw a 7,11 network
                        % First we draw the vertices
                        \foreach \pos/\name in {{(0,2)/a}, {(2,1)/b}, {(4,1)/c},
                              {(0,0)/d}, {(3,0)/e}, {(2,-1)/f}, {(4,-1)/g}}
                              \node[vertex] (\name) at \pos {$\name$};
                        % Connect vertices with edges and draw weights
                        \foreach \source/ \dest in {b/a, c/b,d/a,d/b,
                              e/b, e/c,e/d,
                              f/d,f/e,
                              g/e,g/f}
                        \path[edge] (\source) -- node[weight]{} (\dest);
                  \end{tikzpicture}
                  \label{fig:graphDefinitionExample}
                  \caption{An example of a graph.}
            \end{figure}
      \end{definition}
\end{frame}

\begin{frame}
      \frametitle{Graph Representation Of Characters}
      \begin{definition}\label{def:graphRepresetationOfChannel}
            Given a channel that sending $\{1,2,\dots,n\}$ as characters. And some characters $i$ and $j$ could be confused with each other.

            \smallskip

            Then the graph representation of the characters is the graph with vertices $\{1,2,\dots,n\}$ and edges $(i,j)$ if and only if $i$ and $j$ is \textbf{distinct} and could be \textbf{confused with each other}.
      \end{definition}

      Accordingly, there is the corresponding way that using graphs to represent a message and Shannon Capacity.
\end{frame}

\begin{frame}
      \frametitle{Product Graph}
      
      The product of two graphs can be considered as send a pair of characters $(x,y)$ as one message. So, we have a channel that send messages of for $2$ unit time.

      \pause
      \smallskip

      Recall that before, $2$ distinct messages is confusable means that they can be decoded into the same message, which means every characters the two channel use need to be confusable or the same.

      \begin{definition}[graph product]\label{def:graphProduct}
            Given two graph $ G $ and $ H $. The graph product $ G \times H $ is the graph with vertices $ V(G \times H) = V(G) \times V(H) $ in which $ (x,y) $ is adjacent to $ (x',y') $ in $ G \times H $ if and only if $ x $ is \textbf{adjacent} to $ x' $ or the \textbf{same} in $ G $ and $ y $ is \textbf{adjacent} to $ y' $ or the \textbf{same} in $ H $.

            \pause

            A graph $ G $ product itself for $ n $ times will always be denoted by $ G^n $.

            Which means we could use $ G^n $ to represent messages of a channel that send messages for $n$ unit time.
      \end{definition}
\end{frame}

\begin{frame}
      \frametitle{$\alpha(G)$}
      \begin{definition}[$\alpha(G)$]\label{def:alpha}
            Given a finite graph $G$. $\alpha(G)$ is the \textbf{maximum} number of vertices such that every two of them is not adjacent in $G$.

            If $G$ represent a set of characters, $\sqrt[n]{\alpha(G^{n})}$ is just the zero error rate we have defined before.

            \pause

            \tikzstyle{vertex}=[circle,fill=black!25,minimum size=20pt,inner sep=0pt]
            \tikzstyle{selected vertex}=[circle,fill=red!25,minimum size=20pt,inner sep=0pt]
            \tikzstyle{edge} = [draw,thick,-]
            \tikzstyle{weight} = [font=\small]
            \begin{figure}[h!]
                  \begin{tikzpicture}[scale=1, auto,swap]
                        % Draw a 7,11 network
                        % First we draw the vertices
                        \foreach \pos/\name in {{(0,1)/a}, {(2,1)/b}, {(4,1)/c},
                              {(0,0)/d}, {(3,0)/e}, {(2,-1)/f}, {(4,-1)/g}}
                              \node[vertex] (\name) at \pos {$\name$};
                        \foreach \pos/\name in {{(0,1)/a}, {(4,1)/c},
                              {(2,-1)/f}}
                              \node[selected vertex] (\name) at \pos {$\name$};
                        % Connect vertices with edges and draw weights
                        \foreach \source/ \dest in {b/a, c/b,d/a,d/b,
                              e/b, e/c,e/d,
                              f/d,f/e,
                              g/e,g/f}
                        \path[edge] (\source) -- node[weight]{} (\dest);
                  \end{tikzpicture}
                  \label{fig:alphaGExample}
                  \caption{Example of $ \alpha(G) $. Here $ \alpha(G) = 3 $.}
            \end{figure}
      \end{definition}
\end{frame}
